Checkpoint 4

### 2020-05-01 Draft-Report.Rmd
Update Draft-Report.Rmd

*White, StateColor, Day, Total Test Results, State

@@

```{r}
# Trace plots
mcmc_trace(complexmod)

# Density plots
mcmc_dens_overlay(complexmod)
```
The trace and

```{r}
pp_check(complexmod, nreps = 50)
```
The assumption of using a Normal model is fairly reasonable besides the fact that we observe two bumps on both sides of the tails. We can assume these to be outliars.

```{r}
# Store the chains
model_complex_df <- as.array(complexmod) %>%
  melt %>%
  pivot_wider(names_from = parameters, values_from = value)

@@

@@

>>>>

Variables of Interest: `White`, `StateColor`, `Day`, `Total Test Results`, `State`

@@

```{r}
# Trace plots
mcmc_trace(complexmod,pars = c("sigma","(Intercept)","percent_white","StateColorred","StateColorpurple","positive","Day","b[Day State:AK]","b[Day State:WA]"),facet_args = list(ncol = 3, strip.position = "left"))

# Density plots
mcmc_dens_overlay(complexmod, pars = c("sigma","(Intercept)","percent_white","StateColorred","StateColorpurple","positive","Day","b[Day State:AK]","b[Day State:WA]"),facet_args = list(ncol = 3, strip.position = "left"))
```

**Comment:** For our MCMCs graphs we chose to just look at our predictors, intercept, and sigma value. We sadly cannot visualize all of our random slopes given that we would have over 50. However, we did visualize at least a couple of the random slopes as seen above. From the MCMC Dens and Trace we see that our chains are all close to each other meaning that our simulation was stable, which is great!

```{r}
pp_check(complexmod, nreps = 50)
```
**Comment:** The assumption of using a Normal model is fairly reasonable besides the fact that we observe two bumps on both sides of the tails. We can assume these to be outliars.

```{r}
# Store the chains
model_complex_df <- as.array(complexmod) %>%
  melt %>%
  pivot_wider(names_from = parameters, values_from = value)
model_complex_df

@@

**Comment:** Unfortunately, when we plot the correlation within our dataset we see that it comes out as empty. This can be attributed to the complexity of our model. What we found through our initial visualization exploration is that when we add additional parameters the correlation tends to decrease. This makes sense as a lot of our parameters are specific to each state.

@@

Sofia created the draft report document and organized it so that it would be easier to follow. Along with creating and organizing the document, I helped Quinn and Will write the Introduction. In addition, Quinn and I worked on making the complex model. After we created the model I focused on the model evaluation section for that model, and was able to get our MCMC plots to show.
